
```{r knit-setup, echo=FALSE, results='hide'}
library(knitr)
opts_chunk$set(message=FALSE, warning=FALSE,
               comment="",
               echo=FALSE, results='hide')
opts_knit$set(error = FALSE)
opts_knit$set(progress = TRUE, verbose = TRUE)
# options(rstudio.markdownToHTML =
#   function(inputFile, outputFile) {
#     library(knitrBootstrap)
#     knit_bootstrap_md(input=inputFile, output=outputFile, code_style="Brown Paper", chooser=c("boot", "code"), show_code=FALSE)
#   }
# )
```
 

```{r, echo=FALSE}

rm(list=ls())
library(R.matlab)
library(oro.nifti)
library(plyr)
library(ggplot2)
library(reshape2)
library(RColorBrewer)
library(knitrBootstrap)
library(xtable)
library(scales)
library(fslr)
library(cttools)
### need cairo for cluster
options(bitmapType='cairo')
homedir = "/Applications"
rootdir = "/Volumes/DATA_LOCAL/Image_Processing"
if (Sys.info()[["user"]] %in% "jmuschel") {
  homedir = "~"
  rootdir = "/dexter/disk2/smart/stroke_ct/ident"
}
progdir = file.path(rootdir, "programs")
# source(file.path(progdir, "convert_DICOM.R"))
# source(file.path(progdir, "fslhd.R"))
basedir = file.path(rootdir, "Registration")


#### baseline NIHSSS ata 
nihss = read.csv(file.path(basedir, "baseline_NIHSS.csv"), 
                 stringsAsFactors=FALSE)
tempdir = file.path(rootdir, "Template")
atlasdir = file.path(tempdir, "atlases")

load(file.path(atlasdir, "All_FSL_Atlas_Labels.Rda"))

outdir = file.path(basedir, "results")
whichdir = "reoriented"

# whichdir = "FLIRT"
rerun = FALSE

template = file.path(tempdir, "scct_unsmooth.nii.gz")
temp = readNIfTI(template)

t.t1 = file.path(tempdir, "sct1_unsmooth.nii.gz")
temp.t1 = readNIfTI(t.t1)

setwd(progdir)


all.ids = list.dirs(basedir, recursive=FALSE, full.names=FALSE)
all.ids = all.ids[grepl("\\d\\d\\d-(\\d|)\\d\\d\\d", all.ids)]
redir = file.path(basedir, all.ids, whichdir)
redir = redir[file.exists(redir)]
nfiles = sapply(redir, function(x) 
	length(dir(path=x, pattern="ROI*.nii.*")))
redir = redir[nfiles > 0]
## those that have ROIs
all.ids = gsub(paste0(basedir, "/(.*)/", whichdir), "\\1", redir)

ids.111 = read.csv(file.path(basedir, "111_patients.csv"), stringsAsFactors= FALSE)
all.ids = all.ids[ all.ids %in% ids.111$id ]
# all.ids = all.ids[file.exists(redir)]
uid = as.numeric(gsub("-", "", all.ids))



### get clot location
demog = read.csv(file.path(basedir, 
	"All_180_FollowUp_wDemographics.csv"), 
                 stringsAsFactors=FALSE)
demog$Sex = factor(demog$Gender, levels=c("Female", "Male"))
demog$Diagnostic_ICH = demog$ICH_Dx_10 *10

demog = demog[ demog$patientName %in% uid, ]
dd = demog[ order(demog$patientName), ]
dd = dd[, c("patientName", "Clot_Location_RC")]
colnames(dd) = c("id", "clot_location")


get.overlap <-  function(dman, dauto){
	dman = c(dman > 0)
	dauto = c(dauto > 0)	
	stopifnot(length(dman) == length(dauto))	
	
	ab <- as.numeric(t(dman) %*% dauto)
	plus = dman + dauto
	aplusb <- sum(plus)
	### different way of doing a + b
	aorb <- sum(plus > 0)
	dice <- 2 * ab/aplusb
	jaccard <- ab/aorb 
	
#	tab <- table(cdman, cdauto, dnn=c("dman", "dauto"))
	sens <- mean(dauto[dman]) ##tab[2,2]/sum(tab[2,])
	spec <- mean(!dauto[!dman])
	accur <- mean( dauto == dman )
	res <- c(dice=dice, jaccard=jaccard, sens=sens, spec = spec, accur=accur)
	# print(res)
	return(res)
}


```




```{r templatestuff}

tempmask.fname = file.path(tempdir, "scct_mask.nii.gz")
tempmask = readNIfTI(tempmask.fname)


tempskull = file.path(tempdir, "scct_unsmooth_skull_400_1000.nii.gz")
skullpng = gsub("\\.nii\\.gz", ".png", tempskull)

if (!file.exists(skullpng)){

	tskull = readNIfTI(tempskull)

	png(skullpng, type="cairo")

	orthographic(tskull)

	dev.off()
}

```


```{r}

dtemp = dim(temp)
ID = "100-318"
run.id = function(ID, whichdir, rerun=TRUE, verbose=TRUE){
	### go to id directory
	# if (verbose) print(ID)
	iddir = file.path(basedir, ID)
	redir = file.path(iddir, whichdir)
	if (!file.exists(redir)){
		system(sprintf('mkdir -p "%s"', redir))
	}
	imgs = list.files(pattern='ROI.*.nii', full.names=TRUE, path=redir)
	imgs = imgs[ !grepl("2mm_", imgs)]
	if (grepl("reoriented", whichdir)) imgs = imgs[ grepl("bws", imgs)]
	imgs = imgs[ !grepl("affine9", imgs)]

	rawimgs = gsub("bws", "w", imgs)
	rawimgs = gsub("^ROI_", "", rawimgs)
	rawimgs = gsub("ROI\\.", ".", rawimgs)

	bin.popimg = popimg = array(0, dim=dtemp)

	# rois = lapply(imgs, readNIfTI)
	keep.imgs = 1
	imgs = imgs[keep.imgs]
	nimgs = length(imgs)
	ids = opngs = rawpngs = rep(NA, nimgs)
	dices = matrix(nrow=nimgs, ncol= 5)
	rownames(dices) = imgs
	colnames(dices) = c("dice", "jaccard", "sens", "spec", "accur")

	df = df

	resdir = file.path(redir, "results")
	if (!file.exists(resdir)){
		system(sprintf('mkdir -p "%s"', resdir))
	}
	iimg = 1;

	popimg.fname = file.path(resdir, "Weighted_Sum_Image")
	binimg.fname = file.path(resdir, "Binary_Sum_Image")

	popimg.nii = paste0(popimg.fname, ".nii.gz")
	binimg.nii = paste0(binimg.fname, ".nii.gz")
	# for (iimg in seq(nimgs)){
		# if (verbose) print(iimg)

		id = basename(rawimgs[iimg])
		id = gsub("\\.gz$", "", id)
		iid = id = gsub("\\.nii$", "", id)
		id = gsub("^w", "spm_", id)
		id = gsub("^affine", "flirt_dof", id)

		ids[iimg] = gsub("^(w|affine(9|12)_)", "", iid)
		rawpngs[iimg] = file.path(resdir, paste0("raw_", id, ".png"))
		opngs[iimg] = file.path(resdir, paste0("roi_", id, ".png"))
	

		if (rerun | 
			!file.exists(opngs[iimg]) |
			!file.exists(rawpngs[iimg]) |
			!file.exists(popimg.nii) |
			!file.exists(binimg.nii)
			){

			if (verbose) print(rawimgs[iimg])

			rawimg = readNIfTI(rawimgs[iimg])
			rawimg[is.nan(rawimg) | is.na(rawimg)] = 0
			# rawimg[ rawimg > 100 | rawimg < 0] = 0
			rawmask = rawimg >= 0 & rawimg <= 100
			dices[iimg, ] = get.overlap(tempmask, rawmask)

			if (verbose) print(imgs[iimg])

			img = readNIfTI(imgs[iimg])
			img[is.nan(img) | is.na(img)] = 0
			tt = temp
			tt[ tt >= 99 | tt < 0] = 0
			tt[ img > 0 ] = 100
			popimg = popimg + img
			bin.popimg = bin.popimg + (img > 0)

			## get cross hair information
			chair = round(colMeans(which(img > 0, arr.ind=TRUE)))

			chair[is.nan(chair)] = dtemp[is.nan(chair)]/2
			png(opngs[iimg], type="cairo")

				orthographic(tt, 
					col= c(gray(0), gray(1:60/60), hotmetal(1)), 
					xyz=chair)

			dev.off()

			png(rawpngs[iimg], type="cairo")

				# orthographic(rawimg,  
				# 	xyz=chair)
				mask.overlay(rawimg, img, xyz=chair, 
					col.y=alpha("red", 0.25))

			dev.off()
		}
	# }
	popimg 		= popimg 		/ nimgs
	bin.popimg 	= bin.popimg 	/ nimgs

	dice.fname = file.path(resdir, "DICE_overlap.Rda")
	if (rerun) {
		save(dices, file=dice.fname )
	} else {
		load(dice.fname)
	}
	dices = dices[keep.imgs, ]
	dice.df = data.frame(dices)
	dice.df$id = ids

	if (rerun | 
		!file.exists(popimg.nii) |
		!file.exists(binimg.nii)
		) {
		nim = temp
		nim@.Data = popimg
		nim@cal_min = min(nim, na.rm=TRUE)
		nim@cal_max = max(nim, na.rm=TRUE)
		nim@scl_inter = 0
		nim@scl_slope = 1
  	  	nim@datatype	= 16
  	  	nim@bitpix 		= 32		
		writeNIfTI(nim, filename=popimg.fname)

		nim@.Data = bin.popimg
		nim@cal_min = min(nim, na.rm=TRUE)
		nim@cal_max = max(nim, na.rm=TRUE)
		nim@scl_inter = 0
		nim@scl_slope = 1		
  	  	nim@datatype	= 16
  	  	nim@bitpix 		= 32		
		writeNIfTI(nim, filename=binimg.fname)
	} 
	# if (!rerun){
	# 	popimg = readNIfTI(nim, filename=popimg.fname)
	# 	bin.popimg = readNIfTI(nim, filename=binimg.fname)
	# }

	return(list(nimgs=nimgs, ids=ids, 
		opngs=opngs, rawpngs=rawpngs, 
		popimg.fname=popimg.fname,
		binimg.fname = binimg.fname, 
		dice.df = dice.df))
}

get.popimg = function(res, rerun=TRUE, rescale=TRUE){
	if (rerun){
		bin.popimg = popimg = array(0, dim=dtemp)
		l_ply(res, function(x) {
			tmp = readNIfTI(x$popimg.fname)
			popimg <<- tmp + popimg
			return(NULL)
		}, .progress="text")
		cat("Running Binary Image\n")
		l_ply(res, function(x) {
			tmp = readNIfTI(x$binimg.fname)
			bin.popimg <<- tmp + bin.popimg
			return(NULL)
		}, .progress="text")

		if (rescale){
			nimgs = length(res)
			bin.popimg = bin.popimg / nimgs
			popimg = popimg / nimgs
		}
		return(list(bin.popimg=bin.popimg, popimg=popimg))
	} else {
		return(NULL)
	}
}

get.run = function(res){
	nimgs = sapply(res, function(x) x$nimgs)
	nimgs = sum(nimgs)

	ids = sapply(res, function(x) x$ids)

	opngs = sapply(res, function(x) x$opngs)

	rawpngs = sapply(res, function(x) x$rawpngs)

	dice.df = lapply(res, function(x) x$dice.df)
	dice.df = do.call("rbind", dice.df)

	return(list(nimgs=nimgs, ids=ids, 
		opngs=opngs, rawpngs=rawpngs, dice.df=dice.df))
}

write.popimg = function(img, fname, rerun=TRUE){
	if (rerun){
		nim = temp
		nim@.Data = img
		nim@cal_min = min(nim, na.rm=TRUE)
		nim@cal_max = max(nim, na.rm=TRUE)
		nim@scl_inter = 0
		nim@scl_slope = 1
		nim@datatype	= 16
		nim@bitpix 		= 32		
		writeNIfTI(nim, filename=fname)
	} else {
		fname = gsub("\\.gz$", "", fname)
		fname = gsub("\\.nii$", "", fname)
		fname = paste0(fname, ".nii.gz")
		nim = readNIfTI(fname)
	}
	return(nim)
}

```

```{r spmrundata}

# run1 = run.id("100-318", whichdir=whichdir, rerun=TRUE)
res = llply(all.ids, run.id, whichdir=whichdir, rerun=rerun,
	.progress ="text")
run = get.run(res)
# run = run.data(whichdir, rerun)
nimgs = run$nimgs
stopifnot(length(res) == nimgs)
ids = run$ids
opngs = run$opngs
rawpngs = run$rawpngs
dice.df = run$dice.df


spm.popimg = file.path(outdir, paste0(whichdir, "_Weighted_Sum_Image"))
spm.binimg = file.path(outdir, paste0(whichdir, "_Binary_Sum_Image"))


pop.res = get.popimg(res, rerun=rerun, rescale=TRUE)

##########################################
# Looking at over bad outcomes
##########################################
# aids =  as.numeric(gsub("-", "", all.ids))
# r0.ids = demog$patientName[demog$Bad_Outcome_Day_180 %in% 0]
# r1.ids = demog$patientName[demog$Bad_Outcome_Day_180 %in% 1]

# r0.res = res[aids %in% r0.ids]
# r1.res = res[aids %in% r1.ids]

# r0.img = get.popimg(r0.res, rerun=TRUE, rescale=TRUE)
# r1.img = get.popimg(r1.res, rerun=TRUE, rescale=TRUE)

# r0 = r0.img$popimg
# r1 = r1.img$popimg
# r.diff = r1 - r0

# r0.var = r0*(1-r0)/length(r0.res)
# r1.var = r1*(1-r1)/length(r1.res)

# rdiff.se = sqrt(r0.var + r1.var)
# z.stat = r.diff/rdiff.se
# zabs = abs(z.stat)
# p.data = pnorm(zabs, lower.tail=FALSE)


# na.res = temp
# na.res [!is.na(na.res)] = NA
# res.p = na.res
# sig = p.data
# sig[is.nan(sig)] = 1
# sig.level = 0.05
# res.p[ sig <= sig.level ] = 1
# orthographic(res.p, text = paste0("Level ", sig.level))

# n.r0 = r0 * length(r0.res)
# n.r1 = r1 * length(r1.res)

# res.p2 = na.res
# res.p2[ sig < sig.level & n.r0 > 2 & n.r1 > 2 ] = 1
# orthographic(res.p2, text = paste0("Level ", sig.level))



# dd = array(NA, dim=dim(n.r0))
# dims = dim(dd)
# for (irow in seq(dims[1])){
# 	for (icol in seq(dims[2])){
# 		for (iz in seq(dims[3])){
# 			dd[irow, icol, iz] = prop.test(
# 				x = c(n.r0[irow, icol, iz],
# 					n.r1[irow, icol, iz]),
# 				n = c(length(r0.res),
# 					length(r1.res))
# 			)$p.value
# 		}
# 	}
# }

pop.res = get.popimg(res, rerun=TRUE, rescale=TRUE)

if (rerun){

	if ( is.null(pop.res) ) {
		warning("Rerun should not result in NULL img", 
			immediate. = TRUE)
	}

}

popimg = pop.res$popimg
bin.popimg = pop.res$bin.popimg
popimg = write.popimg(popimg, 
	spm.popimg, 
	rerun = TRUE)
bin.popimg = write.popimg(bin.popimg, 
	spm.binimg, rerun = TRUE)

spm.popimg = paste0(spm.popimg, ".nii.gz")
spm.binimg = paste0(spm.binimg, ".nii.gz")
outfile = file.path(atlasdir, 
  paste0(whichdir, "_All_Atlas_ROI_Overlap_Measures.Rda"))

load(file=outfile)

makeres = function(allres){
	allres$fname = gsub("^bws", "", allres$fname)
	allres$fname = gsub("ROI$", "", allres$fname)
	allres[, c("raw", "bin", "weighted")] = 
		round(allres[, c("raw", "bin", "weighted")] *100, 1)
	ss = strsplit(allres$fname, "_")
	allres$id = sapply(ss, function(x) x[1])
	return(allres)
}
mni.allres = makeres(mni.allres)
tal.allres = makeres(tal.allres)
jhut1.allres = makeres(jhut1.allres)
jhut2.allres = makeres(jhut2.allres)
# allres = allres
# allres$fname = gsub("_ROI", "", allres$fname)
# allres[, c("raw", "bin", "weighted")] = 
# 	round(allres[, c("raw", "bin", "weighted")] *100, 1)

```

# Report 

## Registrations
We used Chris Rorden's [toolbox](http://www.mccauslandcenter.sc.edu/CRNL/clinical-toolbox) to spatially coregistered the CT data to a temmplate, masking out the lesions created from the reading center.We also coregistered using [FLIRT](http://fsl.fmrib.ox.ac.uk/fsl/fslwiki/FLIRT) using the CT Template from the aforementioned toolbox using only the skull, with Hounsfield Units (HU) from 400 to 1000.  Each scan was threshholded and then coregistered using an affine (with 12 degrees of freedom) coregistration.  

### Skull Template Image

```{r, results='asis'}
img.tag = '<img src="%s" alt="%s" style="width: 400px;"/>\n\n'
cat(sprintf(img.tag, skullpng, skullpng))
cat("\n")
```

## Reporting Tools
For each patient, the ROI is overlaid on the template, where the ROI is bright white.  The coregistered image is also printed.  A table of the percent overlap of regions of the ROI on the template (downsampled to 2mm) as were labeled in the [AAL atlas](http://www.ncbi.nlm.nih.gov/pubmed/11771995).  Any region from the ROI was not labeled, was considered "Uncategorized".  

Three measures of overlap were created.  Since the data was downsampled to 2mm, the binary image mask was smoothed/blurred so that not all voxels are 0 or 1.  The three measures are calculated as follows:
1. Voxels with intensity > 0 are summed as in the hemorrhage by region. "Percent Over 0"
2. Voxels with > 0.95 are summmed in the hemorrhage by region. "Percent over 95% Probability"
3. The smoothed values (think of them as probabilities in some sense) are summed by region. "Weighted Sum"

Each region is then scaled by the total number of voxels to give the percent engagement of that region.


```{r catinfo}
pt_to_id = function(x){
	as.numeric(gsub("-", "", x))
}


makebtn = function(viewname, adder){
	btn = paste0('<a class="btn" data-toggle="collapse" data-target="#', 
	viewname, 
	'">View ', adder, ' </a>\n')
}

# makebtn = function(name, adder){
# 	btn = paste0('<a class="btn" data-toggle="collapse" ', 
# 		'data-target="#', name, 
# 	'">View ', adder, ' </a>\n')
# }

cat.table = function(name, id, tops, xtabs){
	cat('<div class="panel panel-default">\n')
	adder = tops[[name]]
	viewname = paste0(id, name)
	cat(makebtn(viewname, 
		paste0(name, ": Top Location: ", adder))
	)
	# cat(makebtn(name, 
	# 	paste0(name, ": Top Location: ", adder))
	# )			
	html.table.attributes = paste0('border = 1, id="', viewname,
		'"')
	print.xtable(xtabs[[name]], type="html", 
		include.rownames=FALSE, comment=FALSE, 
		html.table.attributes = html.table.attributes)
	cat('</div>\n ')

	return(viewname)
}

cat.info = function(){
	ttops = xxtabs = NULL
	my.ids = NULL
	for (iimg in seq(ids)){
		id = ids[iimg]

		nm = names(allreses)
		tops = xtabs = 
			vector(mode = "list", length=length(allreses))
		for (itab in seq(allreses)){
			allres = allreses[[itab]]
			df = allres[ allres$fname == id, ]
			df = df[df$raw != 0, , drop=FALSE]
			df = df[order(df$raw, decreasing=TRUE), , drop=FALSE]
			ID = df$id[1]
			ID = pt_to_id(ID)
			clot.loc = dd[dd$id == ID, "clot_location"]

			agg = aggregate(cbind(raw) ~ area, 
				data=df, sum)
			df = df[, c("area", "raw")]		
			top = df[ order(df$raw, decreasing=TRUE), ]
			top.area = top$area[1]
			colnames(df) = colnames(agg) = c("Area", nm[itab])
			xtabs[[itab]] = xtable(df)
			tops[[itab]] = top.area 
		}

		names(tops) = names(xtabs) = nm

		ss = strsplit(id, "_CT_")[[1]]
		id = ss[1]

		xxtabs = c(xxtabs, xtabs)
		ttops = c(ttops, tops)

		cat(sprintf('## %s\n\n', id))
		img.tag = '<img src="%s" alt="%s" style="width: 400px;display:inline-block;"/>'

		# cat("### Overlaid ROI ##\n\n")
		cat(sprintf(img.tag, opngs[iimg], opngs[iimg]))

		#cat("### Registered Image ##\n\n")
		cat(sprintf(img.tag, rawpngs[iimg], rawpngs[iimg]))

		cat(paste0("\nReading Center location was: ", clot.loc, "\n"))


		my.ids =  c(my.ids, cat.table("MNI", id, tops, xtabs))
		my.ids =  c(my.ids, cat.table("EVE_1", id, tops, xtabs))
		my.ids =  c(my.ids, cat.table("EVE_2", id, tops, xtabs))


		aggxtab = xtable(agg)
		# print.xtable(aggxtab, type="html", include.rownames=FALSE, comment=FALSE)

		cat("\n\n")
	}
	save(tops, xxtabs, file=file.path(outdir, "Per_Patient_Table_Engagement.Rda"))

	return(my.ids)
}

```

# Registration with SPM 

```{r spmrun, results='asis'}
allreses = list(MNI=mni.allres, 
	Talairach=tal.allres, 
	EVE_1 =jhut1.allres, 
	EVE_2 =jhut2.allres)

my.ids = cat.info()
```



# Population Images
## SPM

```{r orthos_spm, results='hide'}

rr = rerun
rr = TRUE
##### write out the pngs
writepng = function(fname, tempimg= NULL, adder ='', rerun=TRUE, 
	text = "", col.y = alpha(hotmetal(10), 0.7), ...){
	pngname = gsub("\\.nii\\.gz", 
		paste0(adder, ".png"), fname)
	if (!file.exists(pngname) | rerun){
		pimg = readNIfTI(fname)
# mask.overlay		
		png(pngname, type="cairo")
		if (is.null(tempimg)) {
			orthographic(pimg, text=text, ...)
		} else {
			mask.overlay(tempimg, pimg, col.y=col.y, ...)
		}
		dev.off()
	}
	return(pngname)
}

centroid = function(img){
	mimg = max(img, na.rm=TRUE)
	max.ind = which(img== mimg, arr.ind=TRUE)
	max.mn = colMeans(max.ind)
	ind = which(img > 0, arr.ind=TRUE)
	cm = colMeans(ind)
	xx = img[img > 0]
	wi = xx/sum(xx)
	wind = ind * wi
	w.mn = colSums(wind)
	return(list(cent=cm, wcent = w.mn, max.mn = max.mn))
}

view.png = function(fname){
	system(sprintf("display %s&", fname))
}

spm1.png = writepng(spm.popimg, adder = "", 
	rerun=rr, text ="Weighted Image")
spm2.png = writepng(spm.binimg, adder = "", 
	rerun=rr, text ="Binary Average")
spm1_hot.png = writepng(spm.popimg, adder = "_heat", 
	rerun=rr,  text ="Weighted Image", 
	col=hotmetal(10))
spm2_hot.png = writepng(spm.binimg, adder = "_heat", 
	rerun=rr, text ="Binary Average", 
	col=hotmetal(10))


spm1_hot_overlay.png = writepng(spm.popimg, tempimg= temp, 
	adder = "_heat_overlay", 
	rerun=rr,  text ="Weighted Image")
spm2_hot_overlay.png = writepng(spm.binimg, tempimg= temp, 
	adder = "_heat_overlay", 
	rerun=rr, text ="Binary Average")

spm1_t1_hot_overlay.png = writepng(spm.popimg, tempimg= temp.t1, 
	adder = "_t1_heat_overlay", window = c(500, 1000),
	rerun=rr,  text ="Weighted Image")
spm2_t1_hot_overlay.png = writepng(spm.binimg, tempimg= temp.t1, 
	adder = "_t1_heat_overlay", window = c(500, 1000),
	rerun=rr, text ="Binary Average")


###########
# TRying divergent palette
#########
coly = alpha(div_gradient_pal(low="blue", 
	mid=muted("red"), 
	high="yellow")(
	seq(0, 1, length=100)
	), .7)
img = readNIfTI(spm.binimg)
center = centroid(img)
spm2_t1_hot_div1.png = writepng(spm.binimg, tempimg= temp.t1, 
	adder = "_t1_heat_diverge_cent", window = c(500, 1000),
	rerun=rr, text ="Weighted Average", col.y=coly,
	xyz=  center$cent)
# view.png(spm2_t1_hot_div.png)
spm2_t1_hot_div2.png = writepng(spm.binimg, tempimg= temp.t1, 
	adder = "_t1_heat_diverge_wcent", window = c(500, 1000),
	rerun=rr, text ="Weighted Average", col.y=coly,
	xyz=  center$wcent)
# view.png(spm2_t1_hot_div.png)

spm2_t1_hot_div3.png = writepng(spm.binimg, tempimg= temp.t1, 
	adder = "_t1_heat_diverge_maxcent", window = c(500, 1000),
	rerun=rr, text ="Weighted Average", col.y=coly,
	xyz=  center$max.mn)

########## 
# TRying a cooler pattern
###########
coly = alpha(div_gradient_pal(low="blue", 
	mid=muted("green"), 
	high="yellow")(
	seq(0, 1, length=100)
	), .7)
spm2_t1_cool_div1.png = writepng(spm.binimg, tempimg= temp.t1, 
	adder = "_t1_cool_diverge_cent", window = c(500, 1000),
	rerun=rr, text ="Weighted Average", col.y=coly,
	xyz=  center$cent)
# view.png(spm2_t1_hot_div.png)
spm2_t1_cool_div2.png = writepng(spm.binimg, tempimg= temp.t1, 
	adder = "_t1_cool_diverge_wcent", window = c(500, 1000),
	rerun=rr, text ="Weighted Average", col.y=coly,
	xyz=  center$wcent)
# view.png(spm2_t1_hot_div.png)

spm2_t1_cool_div3.png = writepng(spm.binimg, tempimg= temp.t1, 
	adder = "_t1_cool_diverge_maxcent", window = c(500, 1000),
	rerun=rr, text ="Weighted Average", col.y=coly,
	xyz=  center$max.mn)
# view.png(spm2_t1_hot_div.png)



```

```{r pop_table, results='hide', echo=FALSE}

# view.png(spm1_t1_hot_overlay.png)
lists = list(mni.list, jhut1.list, jhut2.list)
pop.tab = llply(lists, function(x) {
	tt = tab.area2(popimg, ind.list=x, keepall=TRUE)
}, .progress= "text")
sums = sapply(pop.tab, colSums)
stopifnot(all(diff(sums) == 0))

##### scaling them to %
pop.tab = llply(pop.tab, function(x) {
	x$nvox = x$nvox/sum(x$nvox) * 100
	x = x[order(x$nvox, decreasing=TRUE), , drop=FALSE]
	x$area = rownames(x)
	x
}, .progress= "text")

nm = names(pop.tab) = c("MNI", "EVE_1", "EVE_2")

tops = xtabs = 
	vector(mode = "list", length=length(pop.tab))
for (itab in seq(pop.tab)){
	df = allres = pop.tab[[itab]]
	df$nvox = round(df$nvox, 2)
	df = df[df$nvox != 0, , drop=FALSE]
	top.area = rownames(df)[1]
	df = df[, c("area", "nvox")]		

	colnames(df) = c("Area", nm[itab])
	xtabs[[itab]] = xtable(df)
	tops[[itab]] = top.area 
}
names(tops) = names(xtabs) = nm
id = "Population"
save(tops, xtabs, file=file.path(outdir, "Population_Table_Engagement.Rda"))

```

## Population Breakdown

```{r print_pop_table, results='asis'}

my.ids = c(my.ids, cat.table("MNI", id, tops, xtabs))
my.ids = c(my.ids, cat.table("EVE_1", id, tops, xtabs))
my.ids = c(my.ids, cat.table("EVE_2", id, tops, xtabs))

```

```{r, results='asis'}
img.tag = '<img src="%s" alt="%s" style="width: 400px;float: left;"/>'
cat(sprintf(img.tag, spm1.png, spm1.png))
cat(sprintf(img.tag, spm2.png, spm2.png))
cat(sprintf(img.tag, spm1_hot.png, spm1_hot.png))
cat(sprintf(img.tag, spm2_hot.png, spm2_hot.png))
cat(sprintf(img.tag, spm1_hot_overlay.png, spm2_hot_overlay.png))
cat(sprintf(img.tag, spm1_t1_hot_overlay.png, spm2_t1_hot_overlay.png))
cat(sprintf(img.tag, spm2_t1_hot_div1.png, spm2_t1_hot_div1.png))
cat(sprintf(img.tag, spm2_t1_hot_div3.png, spm2_t1_hot_div3.png))
cat(sprintf(img.tag, spm2_t1_cool_div1.png, spm2_t1_cool_div1.png))
cat(sprintf(img.tag, spm2_t1_cool_div3.png, spm2_t1_cool_div3.png))
cat("\n\n")
```



### Session Info

```{r, echo=TRUE, results='markup'}
sessionInfo()
```

```{r, results='asis'}

cat('<script type="text/javascript">\n')
  # // $('#collapseOne').collapse("hide");
collapser = function(x) {
	cat(paste0("$('#", x, "').collapse(", 
	'"hide"', 
	');\n'))
}
for (iid in seq_along(my.ids)){
	collapser(my.ids[iid])
}
cat('</script>\n')

```
